The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

  The bipolar jets are constantly ejected from a cylindrical source at the beginning of simulation ($t=0$)\
  and suddenly quenched at $t=1.2$ Myr before fully breaking out the disc.\
  Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
  The jet duration (1.2 Myr) allows the total ejected energy to be $1.2\times10^{56}$ erg, bracketed by\
  $8\times10^{55}$ and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\

>>>>

  The bipolar jets are constantly ejected from a cylindrical source at the beginning of simulation ($t=0$)\
  and suddenly quenched at $t=1.2$ Myr before fully breaking out the disc.\
  Without quenching, the Galactic bubbles at the present time will be asymmetric about the Galactic plane.
  The jet duration allows the total ejected energy to be $1.2\times10^{56}$ erg, bracketed by\
  $8\times10^{55}$ and $1.3\times10^{56}$ erg, estimated by \citet{Predehl2020}.\
